---
title: "Community Variability - First Survey"
author: "Rodolfo Pelinson"
date: "20/10/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r 1, eval = FALSE}
install.packages("devtools")
devtools::install_github("RodolfoPelinson/Pelinson.et.al.2020B")
```

```{r 2}
library(Pelinson.et.al.2020B)
```

```{r 3, message=FALSE, warning=FALSE}
library(lme4)
library(car)
library(emmeans)
```
 

### Whole community for the First Surveys.
First loading data
```{r 4}
data(com_SS1, All, fish_SS1, isolation_SS1, fish_isolation_SS1)
```

Computing observed and expected distances to centroid, and beta-deviation.
```{r 5, cache = T, warning=FALSE, message=FALSE}
beta_deviation_SS1 <- beta_deviation(com_SS1, strata = fish_isolation_SS1, times = 10000,
                                      transform = NULL, dist = "bray", fixedmar="both",
                                      shuffle = "both", method = "quasiswap", seed = 2, group = fish_isolation_SS1) 

```


#### Observed Community Variability
Running ANOVA table for observed distances to group centroids, or observed beta-diversity/community variability in each treatment.
```{r 6}
fit_observed_SS1 <- lm(beta_deviation_SS1$observed_distances~fish_SS1*isolation_SS1)
round(Anova(fit_observed_SS1, test.statistic = "F"),3)
```
No effect of treatments.

Plotting it:
```{r 7, dpi = 150, fig.height=5, fig.width=5}
fish_isolation_SS1 <- factor(fish_isolation_SS1, levels = c("030 absent","120 absent", "480 absent","030 present","120 present", "480 present"))

boxplot(beta_deviation_SS1$observed_distances~isolation_SS1*fish_SS1, outline = F, ylab = "Distance to Centroid (Observed)", xlab = "", at = c(1,2,3,5,6,7),ylim = c(0,1), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(fish_isolation_SS1)
levelProportions <- summary(fish_isolation_SS1)/length(beta_deviation_SS1$observed_distances)
col <- c(rep("sienna3",3), rep("dodgerblue3",3))
#bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- beta_deviation_SS1$observed_distances[fish_isolation_SS1==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], cex = 1.5, lwd = 3) 
  
}
boxplot(beta_deviation_SS1$observed_distances~isolation_SS1*fish_SS1, add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7), lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8, at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
box(lwd = 2.5)
```




#### Expected Community Variability
Running ANOVA table for observed distances to group centroids, or observed beta-diversity/community variability in each treatment.
```{r 8}
fit_expected_SS1 <- lm(beta_deviation_SS1$expected_distances~fish_SS1*isolation_SS1)
round(Anova(fit_expected_SS1, test.statistic = "F"),3)
emmeans(fit_expected_SS1, list(pairwise ~ isolation_SS1), adjust = "tukey")
```
There is an increase in expected distance to centroid from intermediate to high isolation.

Plotting it:
```{r 9, dpi = 150, fig.height=5, fig.width=5}
fish_isolation_SS1 <- factor(fish_isolation_SS1, levels = c("030 absent","120 absent", "480 absent","030 present","120 present", "480 present"))

boxplot(beta_deviation_SS1$expected_distances~isolation_SS1*fish_SS1, outline = F, ylab = "Distance to Centroid (Expected)", xlab = "", at = c(1,2,3,5,6,7),ylim = c(0,1), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(fish_isolation_SS1)
levelProportions <- summary(fish_isolation_SS1)/length(beta_deviation_SS1$expected_distances)
col <- c(rep("sienna3",3), rep("dodgerblue3",3))
#bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- beta_deviation_SS1$expected_distances[fish_isolation_SS1==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], cex = 1.5, lwd = 3) 
  
}
boxplot(beta_deviation_SS1$expected_distances~isolation_SS1*fish_SS1, add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7), lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8, at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
box(lwd = 2.5)
```


#### Beta-Deviation
Running ANOVA table for observed distances to group centroids, or observed beta-diversity/community variability in each treatment.
```{r 10}
fit_deviation_SS1 <- lm(beta_deviation_SS1$deviation_distances~fish_SS1*isolation_SS1)
round(Anova(fit_deviation_SS1, test.statistic = "F"),3)
```
No significant effect of treatments.

Plotting it:
```{r 11, dpi = 150, fig.height=5, fig.width=5}
boxplot(beta_deviation_SS1$deviation_distances~isolation_SS1*fish_SS1, outline = F, ylab = "Distance to Centroid (deviation)", xlab = "", at = c(1,2,3,5,6,7),ylim = c(-2,10), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(fish_isolation_SS1)
levelProportions <- summary(fish_isolation_SS1)/length(beta_deviation_SS1$deviation_distances)
col <- c(rep("sienna3",3), rep("dodgerblue3",3))
#bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- beta_deviation_SS1$deviation_distances[fish_isolation_SS1==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], cex = 1.5, lwd = 3) 
  
}
boxplot(beta_deviation_SS1$deviation_distances~isolation_SS1*fish_SS1, add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7), lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8, at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
abline(h = 0, lty = 2, lwd = 2, col = "grey50")
box(lwd = 2.5)
```
