---
title: "Community Size Analyses"
author: "Rodolfo Pelinson"
date: "16/10/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r instaling package, eval = FALSE}
install.packages("devtools")
devtools::install_github("RodolfoPelinson/Pelinson.et.al.2020B")
```

```{r loading the package}
library(Pelinson.et.al.2020B)
```


## Analysis of Community Size

Lets load the necessary packages:
```{r loading packages, warning = F, message = F}
library(lme4)
library(emmeans)
library(car)
```

### Whole Community
First, lets load the necessary data:
```{r loading data}
data(com_SS2_SS3_abundance,
     isolation_SS2_SS3,
     fish_SS2_SS3,
     SS_SS2_SS3,
     ID_SS2_SS3,
     All)
```


Now, lets check what probability distribution should we choose using the most complex model we have:
```{r checking distribution, dpi=150, fig.height=3, fig.width=3}
mix_model_G <- lmer(com_SS2_SS3_abundance~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), REML = F)
mix_model_P <- glmer(com_SS2_SS3_abundance~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), family = "poisson")
mix_model_NB <- glmer.nb(com_SS2_SS3_abundance~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3))

plot(mix_model_G)
plot(mix_model_P)
plot(mix_model_NB)

AIC(mix_model_G,mix_model_P,mix_model_NB)
```
Looking at AIC values and the spread of residuals, it seems like negative binomial is the best option here.

So we can go further analysing the data:
```{r running ab, cache=T}
mix_model_NB <- glmer.nb(com_SS2_SS3_abundance~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3))
Anova(mix_model_NB, test.statistic = "Chisq")
```

Now pairwise differences:
```{r  pw ab, cache = T}
emmeans(mix_model_NB, list(pairwise ~ SS_SS2_SS3), adjust = "sidak")
emmeans(mix_model_NB, list(pairwise ~ SS_SS2_SS3|fish_SS2_SS3), adjust = "sidak")
emmeans(mix_model_NB, list(pairwise ~ SS_SS2_SS3|isolation_SS2_SS3), adjust = "sidak")
```
It seems that community size grows with time. But it grows larger in fishless ponds, and in higher isolation treatments.

Lets plot it:
```{r plotting ab, dpi = 150, fig.height=5, fig.width=5}
isolation_SS <-rep(NA, length(All))
for(i in 1:length(All)){
  if(SS_SS2_SS3[i] == "2" & isolation_SS2_SS3[i] == "30"){isolation_SS[i] <- "2 030"}
  if(SS_SS2_SS3[i] == "2" & isolation_SS2_SS3[i] == "120"){isolation_SS[i] <- "2 120"}
  if(SS_SS2_SS3[i] == "2" & isolation_SS2_SS3[i] == "480"){isolation_SS[i] <- "2 480"}
  if(SS_SS2_SS3[i] == "3" & isolation_SS2_SS3[i] == "30"){isolation_SS[i] <- "3 030"}
  if(SS_SS2_SS3[i] == "3" & isolation_SS2_SS3[i] == "120"){isolation_SS[i] <- "3 120"}
  if(SS_SS2_SS3[i] == "3" & isolation_SS2_SS3[i] == "480"){isolation_SS[i] <- "3 480"}
}
isolation_SS <- as.factor(isolation_SS)
isolation_SS <- factor(isolation_SS, levels = c("2 030", "3 030","2 120", "3 120","2 480", "3 480" ))
new_All <- factor(All, levels = c("2 030 absent","3 030 absent","2 120 absent","3 120 absent","2 480 absent","3 480 absent",
                                  "2 030 present","3 030 present","2 120 present","3 120 present","2 480 present","3 480 present"))

boxplot(com_SS2_SS3_abundance~isolation_SS, outline = F, ylab = "Abundance", xlab = "", at = c(1,2,4,5,7,8), lwd = 1.5, ylim = c(0,1400), col = "transparent", xaxt="n")
mylevels <- levels(new_All)
levelProportions <- summary(new_All)/length(com_SS2_SS3_abundance)
col <-  c(rep(c("sienna3","grey70"),3), rep(c("dodgerblue3","grey70"),3))
bg <- c(rep("sienna3",6), rep("dodgerblue3",6))
pch <- c(15,22,16,21,17,24,15,22,16,21,17,24)
for(i in 1:length(mylevels)){
  
  x <- c(1,2,4,5,7,8,1,2,4,5,7,8)[i]
  thislevel <- mylevels[i]
  thisvalues <- com_SS2_SS3_abundance[new_All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i], cex = 1.5, lwd = 3) 
  
}
axis(1,labels = c("1st", "2nd", "1st", "2nd", "1st", "2nd"), cex.axis = 0.8, at =c(1,2,4,5,7,8))
axis(1,labels = c("30 m","120 m", "480 m"), cex.axis = 1, at =c(1.5,4.5,7.5), line = 1.5, tick = F )
boxplot(com_SS2_SS3_abundance~isolation_SS, add = T, col = "transparent", outline = F,at = c(1,2,4,5,7,8), lwd = 1.5, xaxt="n")
box(lwd = 2.5)

```

### Only Predatory Insects Community
First, lets load the necessary data:
```{r loading data predators}
data(com_SS2_SS3_predators_abundance)
```

Analysing the data:
```{r running ab predators, cache=T}
mix_model_predators_NB <- glmer.nb(com_SS2_SS3_predators_abundance~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), control = glmerControl(optimizer = "bobyqa"))
Anova(mix_model_predators_NB, test.statistic = "Chisq")
```

Now pairwise differences:
```{r  pw abundances predators, cache = T}
emmeans(mix_model_predators_NB, list(pairwise ~ isolation_SS2_SS3), adjust = "sidak")
emmeans(mix_model_predators_NB, list(pairwise ~ fish_SS2_SS3|SS_SS2_SS3), adjust = "sidak")
```
It seems that when we only consider predatory insects, community size is affected by time (survey) presence of fish (which have a stronger effect in the third survey) and isolation.

Lets plot it:
```{r Plotting ab predators, dpi = 150, fig.height=5, fig.width=5}
boxplot(com_SS2_SS3_predators_abundance~isolation_SS2_SS3*fish_SS2_SS3, outline = F, ylab = "Abundance", xlab = "", at = c(1,2,3,5,6,7), lwd = 1.5, ylim = c(0,170), col = "transparent", xaxt="n", main = "Predators")
mylevels <- levels(All)
levelProportions <- summary(All)/length(com_SS2_SS3_predators_abundance)
col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
for(i in 1:length(mylevels)){

  x<- c(1,2,3,5,6,7,1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- com_SS2_SS3_predators_abundance[All==thislevel]

  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3)

}
boxplot(com_SS2_SS3_predators_abundance~isolation_SS2_SS3*fish_SS2_SS3, add = T, outline = F,at = c(1,2,3,5,6,7), lwd = 1.5, col = "transparent", xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8, at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
box(lwd = 2.5)

```


### Only Non-Predatory Insects (Herbivores and Detritivores) Community
First, lets load the necessary data:
```{r loading data non predators}
data(com_SS2_SS3_non_predators_abundance)
```

Analysing the data:
```{r running predators abundance, cache=T}
mix_model_non_predators_NB <- glmer.nb(com_SS2_SS3_non_predators_abundance~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), control = glmerControl(optimizer = "bobyqa"))
Anova(mix_model_non_predators_NB, test.statistic = "Chisq")
```

Now pairwise differences:
```{r  pw_abundances_non_predators, cache = T}
emmeans(mix_model_non_predators_NB, list(pairwise ~ SS_SS2_SS3|isolation_SS2_SS3), adjust = "sidak")
```
It seems that we have similar patterns to when we consider the whole community.

Lets plot it:
```{r Plotting ab non predators, dpi = 150, fig.height=5, fig.width=5}
boxplot(com_SS2_SS3_non_predators_abundance~isolation_SS, outline = F, ylab = "Abundance", xlab = "", at = c(1,2,4,5,7,8), lwd = 1.5, ylim = c(0,1400), col = "transparent", xaxt="n", main = "Non-Predators")
mylevels <- levels(new_All)
levelProportions <- summary(new_All)/length(com_SS2_SS3_non_predators_abundance)
col <-  c(rep(c("sienna3","grey70"),3), rep(c("dodgerblue3","grey70"),3))
bg <- c(rep("sienna3",6), rep("dodgerblue3",6))
pch <- c(15,22,16,21,17,24,15,22,16,21,17,24)
for(i in 1:length(mylevels)){
  
  x <- c(1,2,4,5,7,8,1,2,4,5,7,8)[i]
  thislevel <- mylevels[i]
  thisvalues <- com_SS2_SS3_non_predators_abundance[new_All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i], cex = 1.5, lwd = 3) 
  
}
axis(1,labels = c("1st", "2nd", "1st", "2nd", "1st", "2nd"), cex.axis = 0.8, at =c(1,2,4,5,7,8))
axis(1,labels = c("30 m","120 m", "480 m"), cex.axis = 1, at =c(1.5,4.5,7.5), line = 1.5, tick = F )
boxplot(com_SS2_SS3_non_predators_abundance~isolation_SS, add = T, col = "transparent", outline = F,at = c(1,2,4,5,7,8), lwd = 1.5, xaxt="n")
box(lwd = 2.5)

```
