---
title: "Community Variability Analyses"
author: "Rodolfo Pelinson"
date: "20/10/2020"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is the community variability analyses presented in the main paper.

These are the packages you will need to run this code:
```{r 3, message=FALSE, warning=FALSE}
library(PredatorIsolationStochasticity)

library(lme4) # Version 1.1-23
library(car) # Version 3.0-7
library(emmeans) # Version 1.4.8
library(vegan) # Version 2.5-6
library(DHARMa) # Version 0.3.3.0
```
 

## Community Variability

### Whole community for the last two surveys.

First loading data
```{r loading data}
data(com_SS2_SS3, All, fish_SS2_SS3, isolation_SS2_SS3, SS_SS2_SS3, ID_SS2_SS3,
     fish_isolation_SS2_SS3)
```

Computing observed and expected distances to centroid, and beta-deviation.
```{r computing_betas, message=FALSE, warning=FALSE, cache = TRUE}
beta_deviation_SS2_SS3 <- beta_deviation(com_SS2_SS3, strata = All, times = 10000,
                                      transform = NULL, dist = "bray", fixedmar="both",
                                      shuffle = "both", method = "quasiswap", seed = 2,
                                      group = All) 

```


Looking at residual plots for observed, expected distances to centroids and deviations.
```{r checking distribution, dpi = 150, fig.height=5, fig.width=10}
fit_observed_SS2_SS3_G <- lmer(beta_deviation_SS2_SS3$observed_distances~fish_SS2_SS3*
                                 isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3))

resid_observed <- simulateResiduals(fit_observed_SS2_SS3_G)
plot(resid_observed)


fit_expected_SS2_SS3_G <- lmer(beta_deviation_SS2_SS3$expected_distances~fish_SS2_SS3*
                                 isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), 
                               control = lmerControl(optimizer = c("bobyqa"), restart_edge = TRUE, boundary.tol = 1e-10))


resid_expected <- simulateResiduals(fit_expected_SS2_SS3_G)
plot(resid_expected)


fit_deviation_SS2_SS3_G <- lmer(beta_deviation_SS2_SS3$deviation_distances~fish_SS2_SS3*
                                  isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3))

resid_deviation <- simulateResiduals(fit_deviation_SS2_SS3_G)
plot(resid_deviation)

```
Residual plots are not perfect, but they also does not seem too bad.


#### Observed Community Variability

Running ANOVA table for observed distances to group centroids, or observed beta-diversity/community variability in each treatment.
```{r running_observed}
fit_observed_SS2_SS3 <- lmer(beta_deviation_SS2_SS3$observed_distances~fish_SS2_SS3*
                               isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3))

round(Anova(fit_observed_SS2_SS3, test.statistic = "Chisq"),3)
emmeans(fit_observed_SS2_SS3, list(pairwise ~ isolation_SS2_SS3|fish_SS2_SS3),
        adjust = "sidak")
emmeans(fit_observed_SS2_SS3, list(pairwise ~ isolation_SS2_SS3|SS_SS2_SS3),
        adjust = "sidak")
emmeans(fit_observed_SS2_SS3, list(pairwise ~ SS_SS2_SS3|isolation_SS2_SS3),
        adjust = "sidak")
```
It seems that the effect of isolation is dependent on the presence or absence of fish. When fish is absent, there is no effect of isolation. When it is present, there is a negative effect of isolation.

Plotting it:
```{r plot_observed, dpi = 150, fig.height=5, fig.width=5}
boxplot(beta_deviation_SS2_SS3$observed_distances~isolation_SS2_SS3*fish_SS2_SS3,
        outline = F, ylab = "Distance to Centroid (Observed)", xlab = "",
        at = c(1,2,3,5,6,7),ylim = c(0,1), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(All)
levelProportions <- summary(All)/length(beta_deviation_SS2_SS3$observed_distances)
col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,5,6,7,1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- beta_deviation_SS2_SS3$observed_distances[All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(beta_deviation_SS2_SS3$observed_distances~isolation_SS2_SS3*fish_SS2_SS3,
        add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7),
        lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8,
     at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
box(lwd = 2.5)
```



#### Expected Community Variability

Running ANOVA table for expected distances to group centroids, or expected beta-diversity/community variability in each treatment.
```{r running_expected, message=FALSE, warning=FALSE}
fit_expected_SS2_SS3 <- lmer(beta_deviation_SS2_SS3$expected_distances~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), control = lmerControl(optimizer = "nlminbwrap"))


round(Anova(fit_expected_SS2_SS3, test.statistic = "Chisq"),3)

emmeans(fit_expected_SS2_SS3, list(pairwise ~ isolation_SS2_SS3),
        adjust = "sidak")
emmeans(fit_expected_SS2_SS3, list(pairwise ~ isolation_SS2_SS3|fish_SS2_SS3),
        adjust = "sidak")
emmeans(fit_expected_SS2_SS3, list(pairwise ~ isolation_SS2_SS3|SS_SS2_SS3),
        adjust = "sidak")
emmeans(fit_expected_SS2_SS3, list(pairwise ~ isolation_SS2_SS3|fish_SS2_SS3|SS_SS2_SS3),
        adjust = "sidak")
```

Patterns are similar to those observed for the observed distances to centroid.

Plotting it:
```{r plot_expected, dpi = 150, fig.height=5, fig.width=5}
boxplot(beta_deviation_SS2_SS3$expected_distances~isolation_SS2_SS3*fish_SS2_SS3,
        outline = F, ylab = "Distance to Centroid (Expected)", xlab = "",
        at = c(1,2,3,5,6,7),ylim = c(0,1), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(All)
levelProportions <- summary(All)/length(beta_deviation_SS2_SS3$expected_distances)
col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,5,6,7,1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- beta_deviation_SS2_SS3$expected_distances[All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(beta_deviation_SS2_SS3$expected_distances~isolation_SS2_SS3*fish_SS2_SS3,
        add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7),
        lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8,
     at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
box(lwd = 2.5)
```



#### Beta-Deviation

Running ANOVA table for the deviations of expected distances to group centroids from observed distances.
```{r running_deviation, message=FALSE, warning=FALSE}
fit_deviation_SS2_SS3 <- lmer(beta_deviation_SS2_SS3$deviation_distances~fish_SS2_SS3*
                                isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3),
                              control = lmerControl(optimizer = "nlminbwrap"))
round(Anova(fit_deviation_SS2_SS3, test.statistic = "Chisq"),3)
emmeans(fit_deviation_SS2_SS3, list(pairwise ~ isolation_SS2_SS3|fish_SS2_SS3),
        adjust = "sidak")
```

Beta deviation seems to increase with isolation, but only in fishless ponds.


Plotting it:
```{r plot_deviation, dpi = 150, fig.height=5, fig.width=5}
boxplot(beta_deviation_SS2_SS3$deviation_distances~isolation_SS2_SS3*fish_SS2_SS3,
        outline = F, ylab = "Beta-Deviation", xlab = "", at = c(1,2,3,5,6,7),
        ylim = c(-2,10), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(All)
levelProportions <- summary(All)/length(beta_deviation_SS2_SS3$deviation_distances)
col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,5,6,7,1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- beta_deviation_SS2_SS3$deviation_distances[All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(beta_deviation_SS2_SS3$deviation_distances~isolation_SS2_SS3*fish_SS2_SS3,
        add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7),
        lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8,
     at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
abline(h = 0, lty = 2, lwd = 2, col = "grey50")
box(lwd = 2.5)
```




#### Observed Environmental Variability

##### Multivariate effect of Environmental Variability

Getting the distances
```{r, dpi = 150, fig.height=5, fig.width=10}
env_data_SS2_SS3_st <- decostand(env_data_SS2_SS3, method = "stand", na.rm = TRUE)

env_data_SS2_SS3_dist <- vegdist(env_data_SS2_SS3_st, method = "euclidean", na.rm = TRUE)

betadisper_SS2_SS3 <- betadisper(env_data_SS2_SS3_dist, group = All)
```


Checking model fit

Variability as a function of treatments
```{r, dpi = 150, fig.height=5, fig.width=10}
fit_env_SS2_SS3 <- lmer(betadisper_SS2_SS3$distances~fish_SS2_SS3*
                               isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3))

resid_env <- simulateResiduals(fit_env_SS2_SS3)
plot(resid_env)
```
There is clearly some patterns in the residuals that are not being accounted for by our model.


Observed community variability as a function of environmental variability
```{r, dpi = 150, fig.height=5, fig.width=10}
fit_observed_SS2_SS3_env <- lmer(beta_deviation_SS2_SS3$observed_distances ~ betadisper_SS2_SS3$distances + (1|ID_SS2_SS3))

resid_observed_env <- simulateResiduals(fit_observed_SS2_SS3_env)
plot(resid_observed_env)
```
everything seems ok.


Beta deviation a function of environmental variability
```{r, dpi = 150, fig.height=5, fig.width=10}
fit_deviation_SS2_SS3_env <- lmer(beta_deviation_SS2_SS3$deviation_distances ~ betadisper_SS2_SS3$distances + (1|ID_SS2_SS3))

resid_deviation_env <- simulateResiduals(fit_deviation_SS2_SS3_env)
plot(resid_deviation_env)
```
everything seems ok.


running anovas for each of those models
```{r, dpi = 150, fig.height=5, fig.width=10}
round(Anova(fit_env_SS2_SS3, test.statistic = "Chisq"),3)

round(Anova(fit_observed_SS2_SS3_env, test.statistic = "Chisq"),3)

round(Anova(fit_deviation_SS2_SS3_env, test.statistic = "Chisq"),3)
```
It seems that there is no evidence of any kind of effect of treatments on environmental variabiliy or of environmental variability on community variability or beta deviation



Ploting it:
```{r, dpi = 150, fig.height=5, fig.width=5}
boxplot(betadisper_SS2_SS3$distances~isolation_SS2_SS3*fish_SS2_SS3,
        outline = F, ylab = "Distance to Centroid (Environmental Variability)", xlab = "",
        at = c(1,2,3,5,6,7),ylim = c(0,5), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(All)
levelProportions <- summary(All)/length(betadisper_SS2_SS3$distances)
col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,5,6,7,1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- betadisper_SS2_SS3$distances[All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(betadisper_SS2_SS3$distances~isolation_SS2_SS3*fish_SS2_SS3,
        add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7),
        lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8,
     at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
box(lwd = 2.5)
```


```{r plot_env, dpi = 150, fig.height=5, fig.width=10}
par(mfrow = c(1,2))
plot(beta_deviation_SS2_SS3$observed_distances ~ betadisper_SS2_SS3$distances, pch = 16, ylab = "Distance to Centroid (Observed Comm. Variability)", xlab = "Distance to Centroid (Environmental Variability)")

plot(beta_deviation_SS2_SS3$deviation_distances ~ betadisper_SS2_SS3$distances, pch = 16, ylab = "Beta Deviation", xlab = "Distance to Centroid (Environmental Variability)")
abline(h = 0, lty = 2, col = "grey50", lwd = 2)
```



##### Univariate effect of Environmental Variability

First, we have to built a matrix with all univariate distances, that is, how much each observation of each variable differs from its treatment mean.
```{r}
distances_env_uni <- data.frame(matrix(NA, ncol = ncol(env_data_SS2_SS3_st), nrow = nrow(env_data_SS2_SS3_st)))
for(i in 1:ncol(env_data_SS2_SS3_st)){
  if(anyNA(env_data_SS2_SS3_st[,i])){
     na_position <- match(NA, env_data_SS2_SS3_st[,i]) 
     distances_env_uni_dist <- vegdist(env_data_SS2_SS3_st[-na_position,i], method = "euclidean", na.rm = FALSE)
     betadisper_env_uni <- betadisper(distances_env_uni_dist, group = All[-na_position])
     distances <- betadisper_env_uni$distances
     distances <- append(distances, NA, after=na_position)
     distances_env_uni[,i] <- distances
  }else{
    distances_env_uni_dist <- vegdist(env_data_SS2_SS3_st[,i], method = "euclidean", na.rm = FALSE)
    betadisper_env_uni <- betadisper(distances_env_uni_dist, group = All)
    distances_env_uni[,i] <- betadisper_env_uni$distances
  }
}
colnames(distances_env_uni) <- colnames(env_data_SS2_SS3_st)
```


Now we can run ANOVAS for each environmental variable
```{r}
uni_anova_env <- data.frame(matrix(NA, ncol = ncol(distances_env_uni), nrow = 7))
for(i in 1:ncol(distances_env_uni)){
  fit <- lmer(distances_env_uni[,i]~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3))
  uni_anova_env[,i] <- round(Anova(fit, test.statistic = "Chisq"),3)$`Pr(>Chisq)`
}
rownames(uni_anova_env) <- c("fish", "isolation", "survey", "fish:isolation", "fish:survey", "isolation:survey","fish:isolation:survey")
colnames(uni_anova_env) <- colnames(distances_env_uni)
uni_anova_env
```

Because we are blindly looking for an effect without previous hypothesis for specific variables, it is important to correct p values of each main and interactive effect for multiple comparisons.
```{r}
uni_anova_env_adjusted_p <- uni_anova_env
for(i in 1:nrow(uni_anova_env)){
  uni_anova_env_adjusted_p[i,] <- p.adjust(uni_anova_env_adjusted_p[i,], method = "fdr") 
}
uni_anova_env_adjusted_p <- round(uni_anova_env_adjusted_p, 3)
uni_anova_env_adjusted_p
```
It seems like there is no important clear effects.




Plotting it.
```{r, dpi = 150, fig.height=15, fig.width=7.5}
par(mfrow = c(4,2))
for(j in 1:ncol(distances_env_uni)){
  boxplot(distances_env_uni[,j]~isolation_SS2_SS3*fish_SS2_SS3,
          outline = F, ylab = "Variability", xlab = "",
          at = c(1,2,3,5,6,7), ylim = c(0,max(na.omit(distances_env_uni[,j]))*1.1), lwd = 1, col = "transparent", xaxt="n", main = paste(colnames(distances_env_uni)[j]))
  mylevels <- levels(All)
  levelProportions <- summary(All)/length(distances_env_uni[,j])
  col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
  bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
  pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
  for(i in 1:length(mylevels)){
    
    x<- c(1,2,3,5,6,7,1,2,3,5,6,7)[i]
    thislevel <- mylevels[i]
    thisvalues <- distances_env_uni[,j][All==thislevel]
    
    # take the x-axis indices and add a jitter, proportional to the N in each level
    myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
    points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
    
  }
  boxplot(distances_env_uni[,j]~isolation_SS2_SS3*fish_SS2_SS3,
          add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7),
          lwd = 1, xaxt="n")
  axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8,
       at =c(1,2,3,5,6,7))
  axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
}
```




Lets also check if any if the variability in any of those variables have an effect on observed community variability...
```{r, message=FALSE, warning=FALSE}
uni_anova_env_com <- data.frame(matrix(NA, nrow = ncol(distances_env_uni), ncol = 3))
for(i in 1:ncol(distances_env_uni)){
  fit <- lmer(beta_deviation_SS2_SS3$observed_distances ~ distances_env_uni[,i] + (1|ID_SS2_SS3))
  uni_anova_env_com[i,1] <- fit@beta[2]
  uni_anova_env_com[i,2] <- round(Anova(fit, test.statistic = "Chisq"),3)$`Pr(>Chisq)`
}
uni_anova_env_com[,3] <- p.adjust(uni_anova_env_com[,2], method = "fdr") 
rownames(uni_anova_env_com) <- colnames(env_data_SS2_SS3_st)
colnames(uni_anova_env_com) <- c("estimate","p","adjust.p")
uni_anova_env_com <- round(uni_anova_env_com, 3)
uni_anova_env_com
```

and beta deviation
```{r, message=FALSE, warning=FALSE}
uni_anova_env_dev <- data.frame(matrix(NA, nrow = ncol(distances_env_uni), ncol = 3))
for(i in 1:ncol(distances_env_uni)){
  fit <- lmer(beta_deviation_SS2_SS3$deviation_distances ~ distances_env_uni[,i] + (1|ID_SS2_SS3))
  uni_anova_env_dev[i,1] <- fit@beta[2]
  uni_anova_env_dev[i,2] <- round(Anova(fit, test.statistic = "Chisq"),3)$`Pr(>Chisq)`
}
uni_anova_env_dev[,3] <- p.adjust(uni_anova_env_dev[,2], method = "fdr") 
rownames(uni_anova_env_dev) <- colnames(env_data_SS2_SS3_st)
colnames(uni_anova_env_dev) <- c("estimate","p","adjust.p")
uni_anova_env_dev <-round(uni_anova_env_dev, 3)
uni_anova_env_dev
```
Again. It seems like there is no important clear effects.




We can plot it.
```{r, dpi = 150, fig.height=15, fig.width=7.5}
par(mfrow = c(4,2))
for(i in 1:ncol(distances_env_uni)){
  plot(beta_deviation_SS2_SS3$observed_distances ~ distances_env_uni[,i],
       pch = 16, ylab = "Observed Comm. Variability",
       xlab = "Environmental Variability", main = paste(colnames(distances_env_uni)[i]))
  
}

par(mfrow = c(4,2))
for(i in 1:ncol(distances_env_uni)){
  plot(beta_deviation_SS2_SS3$deviation_distances ~ distances_env_uni[,i],
       pch = 16, ylab = "Beta Deviation",
       xlab = "Environmental Variability", main = paste(colnames(distances_env_uni)[i]))
  
}
```


