---
title: "Alpha Diversity Analyses"
author: "Rodolfo Pelinson"
date: "16/10/2020"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(PredatorIsolationStochasticity)
```


These are the analyses of alpha diversity for the whole communities and separately to predatory and non-predatory insects. These results are not shown in the main paper.

These are the packages you will need to run this code:
```{r loading_packages, warning = F, message = F}
library(lme4) # Version 1.1-23
library(emmeans) # Version 1.4.8
library(car) # Version 3.0-7
library(DHARMa) # Version 0.3.3.0
```


### Whole Community
First, lets load the necessary data:
```{r loading_data}
data(com_SS2_SS3_richness,
     isolation_SS2_SS3,
     fish_SS2_SS3,
     SS_SS2_SS3,
     ID_SS2_SS3,
     All)
```


Now, lets check what probability distribution should we choose using the most complex model we have:
```{r checking_distribution, dpi=300, fig.height=5, fig.width=10, out.height = 490, out.width = 980}
mix_model_G <- lmer(com_SS2_SS3_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 +
                      (1|ID_SS2_SS3))
mix_model_P <- glmer(com_SS2_SS3_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 +
                       (1|ID_SS2_SS3), family = "poisson")
mix_model_NB <- glmer.nb(com_SS2_SS3_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 +
                           (1|ID_SS2_SS3))

resid_model_G <- simulateResiduals(mix_model_G)
plot(resid_model_G)

resid_model_P <- simulateResiduals(mix_model_P)
plot(resid_model_P)

resid_model_NB <- simulateResiduals(mix_model_NB)
plot(resid_model_NB)

AIC(mix_model_G,mix_model_P,mix_model_NB)
```


Analysing the data:
```{r running_rch, cache=T, message=FALSE, warning=FALSE}
mix_model_richness_NB <- lmer(com_SS2_SS3_richness~fish_SS2_SS3*isolation_SS2_SS3*
                                SS_SS2_SS3 + (1|ID_SS2_SS3))
round(Anova(mix_model_richness_NB, test.statistic = "Chisq"),3)
```
It seems like there is only an effect of the presence of fish on species richness.

Lets plot it:
```{r, dpi = 150, fig.height=5, fig.width=5, out.height = 490, out.width = 490, fig.align = "center"}

boxplot(com_SS2_SS3_richness~isolation_SS2_SS3*fish_SS2_SS3,
        outline = F, ylab = "Richness", xlab = "",
        at = c(1,2,3,5,6,7),ylim = c(5,16), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(All)
levelProportions <- summary(All)/length(com_SS2_SS3_richness)
col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,5,6,7,1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- com_SS2_SS3_richness[All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(com_SS2_SS3_richness~isolation_SS2_SS3*fish_SS2_SS3,
        add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7),
        lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8,
     at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )

```

Ploting two surveys separetely
```{r, dpi = 150, fig.height=5, fig.width=10, out.height = 490, out.width = 980, fig.align = "center"}
par(mfrow = c(1,2))
boxplot(com_SS2_SS3_richness[SS_SS2_SS3 == "2"]~isolation_SS2*fish_SS2,
        outline = F, ylab = "Richness", xlab = "",
        at = c(1,2,3,5,6,7),ylim = c(5,16), lwd = 1.5, col = "transparent", xaxt="n", main = "Second Survey")
mylevels <- levels(fish_isolation_SS2)
levelProportions <- summary(fish_isolation_SS2)/length(com_SS2_SS3_richness[SS_SS2_SS3 == "2"])
col <- rep(c("sienna3", "dodgerblue3"),3)
bg <- rep(c("sienna3", "dodgerblue3"),3)
pch <- c(15,15,16,16,17,17) #o outro é 22,21,24
for(i in 1:length(mylevels)){
  
  x<- c(1,5,2,6,3,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- com_SS2_SS3_richness[SS_SS2_SS3 == "2"][fish_isolation_SS2==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(com_SS2_SS3_richness[SS_SS2_SS3 == "2"]~isolation_SS2*fish_SS2,
        add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7),
        lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8,
     at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
#box(lwd = 2.5)



boxplot(com_SS2_SS3_richness[SS_SS2_SS3 == "3"]~isolation_SS3*fish_SS3,
        outline = F, ylab = "Richness", xlab = "",
        at = c(1,2,3,5,6,7),ylim = c(5,16), lwd = 1.5, col = "transparent", xaxt="n", main = "Third Survey")
mylevels <- levels(fish_isolation_SS3)
levelProportions <- summary(fish_isolation_SS3)/length(com_SS2_SS3_richness[SS_SS2_SS3 == "2"])
col <- rep(c("grey70", "grey70"),3)
bg <- rep(c("sienna3", "dodgerblue3"),3)
pch <- c(22,22,21,21,24,24) #o outro é 22,21,24
for(i in 1:length(mylevels)){
  
  x<- c(1,5,2,6,3,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- com_SS2_SS3_richness[SS_SS2_SS3 == "3"][fish_isolation_SS3==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(com_SS2_SS3_richness[SS_SS2_SS3 == "3"]~isolation_SS3*fish_SS3,
        add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7),
        lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8,
     at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
#box(lwd = 2.5)

```

