---
title: "Alpha Diversity Analyses"
author: "Rodolfo Pelinson"
date: "16/10/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


These are the analyses of alpha diversity for the whole communities and separately to predatory and non-predatory insects. These results are not shown in the main paper.

If you haven't, install the package:
```{r 1, eval = FALSE}
install.packages("devtools")
devtools::install_github("RodolfoPelinson/Pelinson.et.al.2020B")
```

These are the packages you will need to run this code:
```{r loading_packages, warning = F, message = F}
library(Pelinson.et.al.2020B)
library(lme4) # Version 1.1-23
library(emmeans) # Version 1.4.8
library(car) # Version 3.0-7
```


### Whole Community
First, lets load the necessary data:
```{r loading_data}
data(com_SS2_SS3_richness,
     isolation_SS2_SS3,
     fish_SS2_SS3,
     SS_SS2_SS3,
     ID_SS2_SS3,
     All)
```


Now, lets check what probability distribution should we choose using the most complex model we have:
```{r checking_distribution, dpi=150, fig.height=3, fig.width=3, message=FALSE, warning=FALSE}
mix_model_G <- lmer(com_SS2_SS3_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), REML = F, control = lmerControl(optimizer = "bobyqa"))
mix_model_P <- glmer(com_SS2_SS3_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), family = "poisson", control = glmerControl(optimizer = "bobyqa"))
mix_model_NB <- glmer.nb(com_SS2_SS3_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), control = glmerControl(optimizer = "bobyqa"))

plot(mix_model_G)
plot(mix_model_P)
plot(mix_model_NB)

AIC(mix_model_G,mix_model_P,mix_model_NB)
```


Analysing the data:
```{r running_rch, cache=T, message=FALSE, warning=FALSE}
mix_model_richness_NB <- lmer(com_SS2_SS3_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), control = lmerControl(optimizer = "bobyqa"))
round(Anova(mix_model_richness_NB, test.statistic = "Chisq"),3)
```
It seems like there is only an effect of the presence of fish on species richness.

Lets plot it:
```{r Plot_rch, dpi = 150, fig.height=5, fig.width=5}
boxplot(com_SS2_SS3_richness~fish_SS2_SS3, outline = F, ylab = "Richness", xlab = "", at = c(1,2), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(All)
levelProportions <- summary(All)/length(com_SS2_SS3_richness)
col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
for(i in 1:length(mylevels)){
  
  x<- c(1,1,1,2,2,2,1,1,1,2,2,2)[i]
  thislevel <- mylevels[i]
  thisvalues <- com_SS2_SS3_richness[All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.3)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(com_SS2_SS3_richness~fish_SS2_SS3, add = T, col = "transparent", outline = F,at = c(1,2), lwd = 1.5, xaxt="n")
axis(1,labels = c("Fishless","Fish"), cex.axis = 1.5, at =c(1,2))

box(lwd = 2.5)
```




### Only Predatory Insects Community
First, lets load the necessary data:
```{r loading_data_pr}
data(com_SS2_SS3_predators_richness)
```

Analysing the data:
```{r running_rch_pr, cache=T, message=FALSE, warning=FALSE}
mix_model_predators_NB <- lmer(com_SS2_SS3_predators_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), control = lmerControl(optimizer = "bobyqa"))
round(Anova(mix_model_predators_NB, test.statistic = "Chisq"),3)
```

Now pairwise differences:
```{r  pw_rch_pr, cache = T}
emmeans(mix_model_predators_NB, list(pairwise ~ isolation_SS2_SS3), adjust = "sidak")
emmeans(mix_model_predators_NB, list(pairwise ~ fish_SS2_SS3|isolation_SS2_SS3|SS_SS2_SS3), adjust = "sidak")
```
It seems like there is an effect of fish and isolation on predatory insect richness. Also, the effect of fish stronger in low isolation treatments in the second survey, and stronger in high isolation treatments in the third survey.


Lets plot it:
```{r Plotting_rch_pr, dpi = 150, fig.height=5, fig.width=10}
boxplot(com_SS2_SS3_predators_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3, outline = F, ylab = "Richness", xlab = "", lwd = 1.5, ylim = c(0,8), col = "transparent", main = "Predators", at = c(1,2,4,5,7,8,10,11,13,14,16,17), xaxt="n")

All2 <- factor(All, levels = c("2 030 absent","2 030 present","2 120 absent","2 120 present","2 480 absent","2 480 present",
                               "3 030 absent","3 030 present","3 120 absent","3 120 present","3 480 absent","3 480 present"))

mylevels <- levels(All2)
levelProportions <- summary(All2)/length(com_SS2_SS3_predators_richness)
col <- c(rep(c("sienna3","dodgerblue3"),3), rep("grey70",6))
bg <- c(rep(c("sienna3","dodgerblue3"),3),rep(c("sienna3","dodgerblue3"),3))
pch <- c(15,15,16,16,17,17,22,22,21,21,24,24)
for(i in 1:length(mylevels)){

  x<- c(1,2,4,5,7,8,10,11,13,14,16,17)[i]
  thislevel <- mylevels[i]
  thisvalues <- com_SS2_SS3_predators_richness[All==thislevel]

  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3)

}
boxplot(com_SS2_SS3_predators_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3, add = T, outline = F,at = c(1,2,4,5,7,8,10,11,13,14,16,17), lwd = 1.5, col = "transparent", xaxt="n")
axis(1,labels = c("Abs.","Pre.", "Abs.","Pre.","Abs.","Pre.","Abs.","Pre.", "Abs.","Pre.","Abs.","Pre."), cex.axis = 0.8, at =c(1,2,4,5,7,8,10,11,13,14,16,17))
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 1, at =c(1.5,4.5,7.5,10.5,13.5,16.5), line = 1.5, tick = F )
axis(1,labels = c("Second","Third"), cex.axis = 1.2, at =c(4.5,13.5), line = 3, tick = F )
box(lwd = 2.5)

```





### Only Non-Predatory Insects Community
First, lets load the necessary data:
```{r loading_data_non_pr}
data(com_SS2_SS3_non_predators_richness)
```

Analysing the data:
```{r rch_non_pr, cache=T, message=FALSE, warning=FALSE}
mix_model_non_predators <- lmer(com_SS2_SS3_non_predators_richness~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), control = lmerControl(optimizer = "bobyqa"))
round(Anova(mix_model_non_predators, test.statistic = "Chisq"),3)
```

Now pairwise differences:
```{r  pw_rch_non_pr, cache = T}
emmeans(mix_model_non_predators, list(pairwise ~ isolation_SS2_SS3|SS_SS2_SS3), adjust = "sidak")
```
It seems like there is an increase in richness from the low to intermediate isolation, but not to high isolation. However, it only happened in the last survey.


Lets plot it:
```{r Plot_rch_non_pr, dpi = 150, fig.height=5, fig.width=5}
boxplot(com_SS2_SS3_non_predators_richness~isolation_SS2_SS3*SS_SS2_SS3, outline = F, ylab = "Richness", xlab = "", at = c(1,2,3,5,6,7), lwd = 1.5, col = "transparent", xaxt="n", main = "Non Predators")
mylevels <- levels(All)
levelProportions <- summary(All)/length(com_SS2_SS3_non_predators_richness)
col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,1,2,3,5,6,7,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- com_SS2_SS3_non_predators_richness[All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.3)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(com_SS2_SS3_non_predators_richness~isolation_SS2_SS3*SS_SS2_SS3, add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7), lwd = 1.5,  xaxt="n") 
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8, at =c(1,2,3,5,6,7))
axis(1,labels = c("Second","Third"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
box(lwd = 2.5)
```
