---
title: "Community Variability - Siqueira et al 2020"
author: "Rodolfo Pelinson"
date: "20/10/2020"
output: github_document
---

```{r 1 setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is the same community variability analyses presented in the main paper, but using a different null model. The same one as used in  [Siqueira et al. 2020](https://doi.org/10.1002/ecy.3014)

If you haven't, install the package:
```{r 2, eval = FALSE}
install.packages("devtools") 
devtools::install_github("RodolfoPelinson/Pelinson.et.al.2020B")
```

These are the packages you will need to run this code:
```{r 4, message=FALSE, warning=FALSE}
library(Pelinson.et.al.2020B)
library(lme4) # Version 1.1-23
library(car) # Version 3.0-7
library(emmeans) # Version 1.4.8
library(vegan) # Version 2.5-6
```
 

## Community Variability

### Whole community for the last two surveys.
First loading data
```{r 5}
data(com_SS2_SS3, All, fish_SS2_SS3, isolation_SS2_SS3, SS_SS2_SS3, ID_SS2_SS3)
```

Computing observed and expected distances to centroid, and beta-deviation.
```{r 6, message=FALSE, warning=FALSE, cache=T}
beta_deviation_SS2_SS3 <- beta_deviation_siqueira_et_al_2019(com_SS2_SS3, times = 10000,
                                                          transform = NULL, dist = "bray", seed = 2, group = All, keep.gamma = T) 

```


Looking at residual plots for observed, expected distances to centroids and deviations.
```{r 7, dpi = 150, fig.height=3, fig.width=3}
fit_expected_SS2_SS3_G <- lmer(beta_deviation_SS2_SS3$expected_distances~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3))
plot(fit_expected_SS2_SS3_G)
qqnorm(resid(fit_expected_SS2_SS3_G, type = "pearson"))
qqline(resid(fit_expected_SS2_SS3_G, type = "pearson"))

fit_deviation_SS2_SS3_G <- lmer(beta_deviation_SS2_SS3$deviation_distances~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3))
plot(fit_deviation_SS2_SS3_G)
qqnorm(resid(fit_deviation_SS2_SS3_G, type = "pearson"))
qqline(resid(fit_deviation_SS2_SS3_G, type = "pearson"))
```

The fit of the model for beta deviation here is pretty bad. If we were to make inferences based on these results, we would have to look for a better statistical model, maybe considering a different statistical distribution, which is hard given that we have overdispersion and negative values (i.e. excludes some distributions and data transformations). But, since we are not interpreting results based on this model, we will still use it.



#### Expected Community Variability
Running ANOVA table for expected distances to group centroids, or expected beta-diversity/community variability in each treatment.
```{r 8, message=FALSE, warning=FALSE}
fit_expected_SS2_SS3 <- lmer(beta_deviation_SS2_SS3$expected_distances~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), control = lmerControl(optimizer = "nlminbwrap"))
round(Anova(fit_expected_SS2_SS3, test.statistic = "Chisq"),3)
emmeans(fit_expected_SS2_SS3, list(pairwise ~ SS_SS2_SS3), adjust = "sidak")
emmeans(fit_expected_SS2_SS3, list(pairwise ~ isolation_SS2_SS3|fish_SS2_SS3), adjust = "sidak")
emmeans(fit_expected_SS2_SS3, list(pairwise ~ isolation_SS2_SS3|SS_SS2_SS3), adjust = "sidak")
emmeans(fit_expected_SS2_SS3, list(pairwise ~ isolation_SS2_SS3|fish_SS2_SS3|SS_SS2_SS3), adjust = "sidak")

```
Patterns are similar to those observed for the observed distances using the other null model.

Plotting it:
```{r 9, dpi = 150, fig.height=5, fig.width=5}
boxplot(beta_deviation_SS2_SS3$expected_distances~isolation_SS2_SS3*fish_SS2_SS3, outline = F, ylab = "Distance to Centroid (Expected)", xlab = "", at = c(1,2,3,5,6,7),ylim = c(0,1), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(All)
levelProportions <- summary(All)/length(beta_deviation_SS2_SS3$expected_distances)
col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,5,6,7,1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- beta_deviation_SS2_SS3$expected_distances[All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(beta_deviation_SS2_SS3$expected_distances~isolation_SS2_SS3*fish_SS2_SS3, add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7), lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8, at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
box(lwd = 2.5)
```



#### Beta-Deviation
Running ANOVA table for the deviations of expected distances to group centroids from observed distances.
```{r 10, message=FALSE, warning=FALSE}
fit_deviation_SS2_SS3 <- lmer(beta_deviation_SS2_SS3$deviation_distances~fish_SS2_SS3*isolation_SS2_SS3*SS_SS2_SS3 + (1|ID_SS2_SS3), control = lmerControl(optimizer = "nlminbwrap"))
round(Anova(fit_deviation_SS2_SS3, test.statistic = "Chisq"),3)
emmeans(fit_deviation_SS2_SS3, list(pairwise ~ SS_SS2_SS3), adjust = "sidak")
emmeans(fit_deviation_SS2_SS3, list(pairwise ~ fish_SS2_SS3|SS_SS2_SS3), adjust = "sidak")
emmeans(fit_deviation_SS2_SS3, list(pairwise ~ isolation_SS2_SS3|SS_SS2_SS3), adjust = "sidak")

```
Beta-deviation seems to be greater in fishless ponds, and in the higher isolation treatment. **But, as we know by inspecting the residuals, this model have a very poor fit.**


Plotting it:
```{r 11, dpi = 150, fig.height=5, fig.width=5}
boxplot(beta_deviation_SS2_SS3$deviation_distances~isolation_SS2_SS3*fish_SS2_SS3, outline = F, ylab = "Beta-Deviation", xlab = "", at = c(1,2,3,5,6,7),ylim = c(-20,180), lwd = 1.5, col = "transparent", xaxt="n")
mylevels <- levels(All)
levelProportions <- summary(All)/length(beta_deviation_SS2_SS3$deviation_distances)
col <- c(rep("sienna3",3), rep("dodgerblue3",3), rep("grey70",6))
bg <- c(rep("sienna3",3), rep("dodgerblue3",3),rep("sienna3",3), rep("dodgerblue3",3))
pch <- c(15,16,17,15,16,17,22,21,24,22,21,24)
for(i in 1:length(mylevels)){
  
  x<- c(1,2,3,5,6,7,1,2,3,5,6,7)[i]
  thislevel <- mylevels[i]
  thisvalues <- beta_deviation_SS2_SS3$deviation_distances[All==thislevel]
  
  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.8)
  points(myjitter, thisvalues, pch=pch[i], col=col[i], bg = bg[i] , cex = 1.5, lwd = 3) 
  
}
boxplot(beta_deviation_SS2_SS3$deviation_distances~isolation_SS2_SS3*fish_SS2_SS3, add = T, col = "transparent", outline = F,at = c(1,2,3,5,6,7), lwd = 1.5, xaxt="n")
axis(1,labels = c("30 m","120 m", "480 m","30 m","120 m", "480 m"), cex.axis = 0.8, at =c(1,2,3,5,6,7))
axis(1,labels = c("Fishless","Fish"), cex.axis = 1, at =c(2,6), line = 1.5, tick = F )
abline(h = 0, lty = 2, lwd = 2, col = "grey50")
box(lwd = 2.5)
```


