---
title: "Gamma Diversity Analyses"
author: "Rodolfo Pelinson"
date: "19/10/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


These are the analyses of gamma diversity for the whole communities (shown in the main paper) and separately to predatory and non-predatory insects.

If you haven't, install the package:
```{r 1, eval = FALSE}
install.packages("devtools")
devtools::install_github("RodolfoPelinson/Pelinson.et.al.2020B")
```

These are the packages you will need to run this code:
```{r loading_packages, warning = F, message = F}
library(Pelinson.et.al.2020B)
library(iNEXT) # Version 2.0.20
library(vegan) # Version 2.5-6
```


### Whole Community
First, lets load the necessary data:
```{r 2}
data(com_SS1, fish_SS1, isolation_SS1, fish_isolation_SS1,
     com_SS2, fish_SS2, isolation_SS2, fish_isolation_SS2,
     com_SS3, fish_SS3, isolation_SS3, fish_isolation_SS3)
```


#### First Survey
First we get the estimated gamma diversity for each treatment for a sample size of four ponds.

First we computed the number of species in each treatment for a similar number of sampled ponds and its respective 95% confidence interval through sample-based rarefaction and extrapolation using the package `iNEXT`. What we call gamma diversity here is the realized species pool that is able to colonize ponds of a given treatment.
```{r 3, cache = T}
absent_30_SS1 <- as.incfreq(t(decostand(com_SS1[which(fish_isolation_SS1 == "030 absent"),], method = "pa")))
present_30_SS1 <- as.incfreq(t(decostand(com_SS1[which(fish_isolation_SS1 == "030 present"),], method = "pa")))
absent_120_SS1 <- as.incfreq(t(decostand(com_SS1[which(fish_isolation_SS1 == "120 absent"),], method = "pa")))
present_120_SS1 <- as.incfreq(t(decostand(com_SS1[which(fish_isolation_SS1 == "120 present"),], method = "pa")))
absent_480_SS1 <- as.incfreq(t(decostand(com_SS1[which(fish_isolation_SS1 == "480 absent"),], method = "pa")))
present_480_SS1 <- as.incfreq(t(decostand(com_SS1[which(fish_isolation_SS1 == "480 present"),], method = "pa")))

all <- list(absent_30=absent_30_SS1 ,absent_120 =absent_120_SS1, absent_480=absent_480_SS1, present_30=present_30_SS1,present_120=present_120_SS1,present_480=present_480_SS1)

SS1_iNEXT <- iNEXT(all, datatype = "incidence_freq", q = 0, knots = 40,se = T, conf = 0.95,nboot =10000, size = c(1:4))

Gamma_SS1 <- rbind(absent_30 = SS1_iNEXT$iNextEst$absent_30[4,c(4,5,6)],
               absent_120 = SS1_iNEXT$iNextEst$absent_120[4,c(4,5,6)],
               absent_480 = SS1_iNEXT$iNextEst$absent_480[4,c(4,5,6)],
               present_30 = SS1_iNEXT$iNextEst$present_30[4,c(4,5,6)],
               present_120 = SS1_iNEXT$iNextEst$present_120[4,c(4,5,6)],
               present_480 = SS1_iNEXT$iNextEst$present_480[4,c(4,5,6)])
```

We can plot the estimates and respective confidence intervals.
```{r 4, dpi = 150, fig.height=5, fig.width=5}
plot(c(NA,NA,NA,NA,NA,NA),ylim = c(0,20), xlim = c(0.5,7.5),type = "p", xaxt = "n",ylab = "Gamma",xlab = "", cex.lab = 1, cex.axis = 1, main = "First Survey")
arrows(y0 = c(Gamma_SS1$qD.LCL[1],Gamma_SS1$qD.LCL[2], Gamma_SS1$qD.LCL[3],Gamma_SS1$qD.LCL[4],Gamma_SS1$qD.LCL[5], Gamma_SS1$qD.LCL[6]),
       y1 = c(Gamma_SS1$qD.UCL[1],Gamma_SS1$qD.UCL[2], Gamma_SS1$qD.UCL[3],Gamma_SS1$qD.UCL[4],Gamma_SS1$qD.UCL[5], Gamma_SS1$qD.UCL[6]),
       x1 = c(1,2,3,5,6,7), x0 = c(1,2,3,5,6,7), 
       code = 3, angle = 90, length = 0.05, c("grey50"), lwd = 2)
points(y = c(Gamma_SS1$qD[1],Gamma_SS1$qD[2], Gamma_SS1$qD[3],Gamma_SS1$qD[4],Gamma_SS1$qD[5], Gamma_SS1$qD[6]), x = c(1,2,3,5,6,7), cex = 2, pch = c(15,16,17), col = c("sienna1","sienna3","sienna4","dodgerblue1","dodgerblue3", "dodgerblue4"))
axis(1, at = c(1,2,3,5,6,7), labels = c("30m ","120m","480m","30m","120m","480m"), las = 1, cex.axis = 1)
axis(1, at = c(2,6), labels = c("Fishless ","Fish"), las = 1, cex.axis = 1, line = 2, tick = F)
box(lwd = 2.5)
```

It does not seem to be any important differences among treatments.


#### Second Survey
First we get the estimated gamma diversity for each treatment for a sample size of four ponds.

First we computed the number of species in each treatment for a similar number of sampled ponds and its respective 95% confidence interval through sample-based rarefaction and extrapolation using the package `iNEXT`. What we call gamma diversity here is the realized species pool that is able to colonize ponds of a given treatment.
```{r 5, cache = T}
absent_30_SS2 <- as.incfreq(t(decostand(com_SS2[which(fish_isolation_SS2 == "030 absent"),], method = "pa")))
present_30_SS2 <- as.incfreq(t(decostand(com_SS2[which(fish_isolation_SS2 == "030 present"),], method = "pa")))
absent_120_SS2 <- as.incfreq(t(decostand(com_SS2[which(fish_isolation_SS2 == "120 absent"),], method = "pa")))
present_120_SS2 <- as.incfreq(t(decostand(com_SS2[which(fish_isolation_SS2 == "120 present"),], method = "pa")))
absent_480_SS2 <- as.incfreq(t(decostand(com_SS2[which(fish_isolation_SS2 == "480 absent"),], method = "pa")))
present_480_SS2 <- as.incfreq(t(decostand(com_SS2[which(fish_isolation_SS2 == "480 present"),], method = "pa")))

all <- list(absent_30=absent_30_SS2 ,absent_120 =absent_120_SS2, absent_480=absent_480_SS2, present_30=present_30_SS2,present_120=present_120_SS2,present_480=present_480_SS2)

SS2_iNEXT <- iNEXT(all, datatype = "incidence_freq", q = 0, knots = 40,se = T, conf = 0.95,nboot =10000, size = c(1:4))

Gamma_SS2 <- rbind(absent_30 = SS2_iNEXT$iNextEst$absent_30[4,c(4,5,6)],
               absent_120 = SS2_iNEXT$iNextEst$absent_120[4,c(4,5,6)],
               absent_480 = SS2_iNEXT$iNextEst$absent_480[4,c(4,5,6)],
               present_30 = SS2_iNEXT$iNextEst$present_30[4,c(4,5,6)],
               present_120 = SS2_iNEXT$iNextEst$present_120[4,c(4,5,6)],
               present_480 = SS2_iNEXT$iNextEst$present_480[4,c(4,5,6)])
```

We can plot the estimates and respective confidence intervals.
```{r 6, dpi = 150, fig.height=5, fig.width=5}
plot(c(NA,NA,NA,NA,NA,NA),ylim = c(10,30), xlim = c(0.5,7.5),type = "p", xaxt = "n",ylab = "Gamma",xlab = "", cex.lab = 1, cex.axis = 1, main = "Second Survey")
arrows(y0 = c(Gamma_SS2$qD.LCL[1],Gamma_SS2$qD.LCL[2], Gamma_SS2$qD.LCL[3],Gamma_SS2$qD.LCL[4],Gamma_SS2$qD.LCL[5], Gamma_SS2$qD.LCL[6]),
       y1 = c(Gamma_SS2$qD.UCL[1],Gamma_SS2$qD.UCL[2], Gamma_SS2$qD.UCL[3],Gamma_SS2$qD.UCL[4],Gamma_SS2$qD.UCL[5], Gamma_SS2$qD.UCL[6]),
       x1 = c(1,2,3,5,6,7), x0 = c(1,2,3,5,6,7), 
       code = 3, angle = 90, length = 0.05, c("grey50"), lwd = 2)
points(y = c(Gamma_SS2$qD[1],Gamma_SS2$qD[2], Gamma_SS2$qD[3],Gamma_SS2$qD[4],Gamma_SS2$qD[5], Gamma_SS2$qD[6]), x = c(1,2,3,5,6,7), cex = 2, pch = c(15,16,17), col = c("sienna1","sienna3","sienna4","dodgerblue1","dodgerblue3", "dodgerblue4"))
axis(1, at = c(1,2,3,5,6,7), labels = c("30m ","120m","480m","30m","120m","480m"), las = 1, cex.axis = 1)
axis(1, at = c(2,6), labels = c("Fishless ","Fish"), las = 1, cex.axis = 1, line = 2, tick = F)
box(lwd = 2.5)
```

It does not seem to be any important differences among treatments.


#### Third Survey
First we get the estimated gamma diversity for each treatment for a sample size of four ponds.

First we computed the number of species in each treatment for a similar number of sampled ponds and its respective 95% confidence interval through sample-based rarefaction and extrapolation using the package `iNEXT`. What we call gamma diversity here is the realized species pool that is able to colonize ponds of a given treatment.
```{r 7, cache = T}
absent_30_SS3 <- as.incfreq(t(decostand(com_SS3[which(fish_isolation_SS3 == "030 absent"),], method = "pa")))
present_30_SS3 <- as.incfreq(t(decostand(com_SS3[which(fish_isolation_SS3 == "030 present"),], method = "pa")))
absent_120_SS3 <- as.incfreq(t(decostand(com_SS3[which(fish_isolation_SS3 == "120 absent"),], method = "pa")))
present_120_SS3 <- as.incfreq(t(decostand(com_SS3[which(fish_isolation_SS3 == "120 present"),], method = "pa")))
absent_480_SS3 <- as.incfreq(t(decostand(com_SS3[which(fish_isolation_SS3 == "480 absent"),], method = "pa")))
present_480_SS3 <- as.incfreq(t(decostand(com_SS3[which(fish_isolation_SS3 == "480 present"),], method = "pa")))

all <- list(absent_30=absent_30_SS3 ,absent_120 =absent_120_SS3, absent_480=absent_480_SS3, present_30=present_30_SS3,present_120=present_120_SS3,present_480=present_480_SS3)

SS3_iNEXT <- iNEXT(all, datatype = "incidence_freq", q = 0, knots = 40,se = T, conf = 0.95,nboot =10000, size = c(1:4))

Gamma_SS3 <- rbind(absent_30 = SS3_iNEXT$iNextEst$absent_30[4,c(4,5,6)],
               absent_120 = SS3_iNEXT$iNextEst$absent_120[4,c(4,5,6)],
               absent_480 = SS3_iNEXT$iNextEst$absent_480[4,c(4,5,6)],
               present_30 = SS3_iNEXT$iNextEst$present_30[4,c(4,5,6)],
               present_120 = SS3_iNEXT$iNextEst$present_120[4,c(4,5,6)],
               present_480 = SS3_iNEXT$iNextEst$present_480[4,c(4,5,6)])
```

We can plot the estimates and respective confidence intervals.
```{r 8, dpi = 150, fig.height=5, fig.width=5}
plot(c(NA,NA,NA,NA,NA,NA),ylim = c(10,30), xlim = c(0.5,7.5),type = "p", xaxt = "n",ylab = "Gamma",xlab = "", cex.lab = 1, cex.axis = 1, main = "Third Survey")
arrows(y0 = c(Gamma_SS3$qD.LCL[1],Gamma_SS3$qD.LCL[2], Gamma_SS3$qD.LCL[3],Gamma_SS3$qD.LCL[4],Gamma_SS3$qD.LCL[5], Gamma_SS3$qD.LCL[6]),
       y1 = c(Gamma_SS3$qD.UCL[1],Gamma_SS3$qD.UCL[2], Gamma_SS3$qD.UCL[3],Gamma_SS3$qD.UCL[4],Gamma_SS3$qD.UCL[5], Gamma_SS3$qD.UCL[6]),
       x1 = c(1,2,3,5,6,7), x0 = c(1,2,3,5,6,7), 
       code = 3, angle = 90, length = 0.05, c("grey50"), lwd = 2)
points(y = c(Gamma_SS3$qD[1],Gamma_SS3$qD[2], Gamma_SS3$qD[3],Gamma_SS3$qD[4],Gamma_SS3$qD[5], Gamma_SS3$qD[6]), x = c(1,2,3,5,6,7), cex = 2, pch = c(15,16,17), col = c("sienna1","sienna3","sienna4","dodgerblue1","dodgerblue3", "dodgerblue4"))
axis(1, at = c(1,2,3,5,6,7), labels = c("30m ","120m","480m","30m","120m","480m"), las = 1, cex.axis = 1)
axis(1, at = c(2,6), labels = c("Fishless ","Fish"), las = 1, cex.axis = 1, line = 2, tick = F)
box(lwd = 2.5)
```
It seems that there is a higher gamma diversity in the intermediate isolation treatment for fishless ponds.




### Predatory Insects
First, lets load the necessary data:
```{r loading_data}
data(com_SS2_predators,com_SS3_predators)
```


#### Second Survey
First we get the estimated gamma diversity for each treatment for a sample size of four ponds.

First we computed the number of species in each treatment for a similar number of sampled ponds and its respective 95% confidence interval through sample-based rarefaction and extrapolation using the package `iNEXT`. What we call gamma diversity here is the realized species pool that is able to colonize ponds of a given treatment.
```{r gamma_SS2, cache = T}
absent_30_SS2 <- as.incfreq(t(decostand(com_SS2_predators[which(fish_isolation_SS2 == "030 absent"),], method = "pa")))
present_30_SS2 <- as.incfreq(t(decostand(com_SS2_predators[which(fish_isolation_SS2 == "030 present"),], method = "pa")))
absent_120_SS2 <- as.incfreq(t(decostand(com_SS2_predators[which(fish_isolation_SS2 == "120 absent"),], method = "pa")))
present_120_SS2 <- as.incfreq(t(decostand(com_SS2_predators[which(fish_isolation_SS2 == "120 present"),], method = "pa")))
absent_480_SS2 <- as.incfreq(t(decostand(com_SS2_predators[which(fish_isolation_SS2 == "480 absent"),], method = "pa")))
present_480_SS2 <- as.incfreq(t(decostand(com_SS2_predators[which(fish_isolation_SS2 == "480 present"),], method = "pa")))

all <- list(absent_30=absent_30_SS2 ,absent_120 =absent_120_SS2, absent_480=absent_480_SS2, present_30=present_30_SS2,present_120=present_120_SS2,present_480=present_480_SS2)

SS2_iNEXT <- iNEXT(all, datatype = "incidence_freq", q = 0, knots = 40,se = T, conf = 0.95,nboot =10000, size = c(1:4))

Gamma_SS2 <- rbind(absent_30 = SS2_iNEXT$iNextEst$absent_30[4,c(4,5,6)],
               absent_120 = SS2_iNEXT$iNextEst$absent_120[4,c(4,5,6)],
               absent_480 = SS2_iNEXT$iNextEst$absent_480[4,c(4,5,6)],
               present_30 = SS2_iNEXT$iNextEst$present_30[4,c(4,5,6)],
               present_120 = SS2_iNEXT$iNextEst$present_120[4,c(4,5,6)],
               present_480 = SS2_iNEXT$iNextEst$present_480[4,c(4,5,6)])
```

We can plot the estimates and respective confidence intervals.
```{r plot_SS2, dpi = 150, fig.height=5, fig.width=5}
plot(c(NA,NA,NA,NA,NA,NA),ylim = c(0,10), xlim = c(0.5,7.5),type = "p", xaxt = "n",ylab = "Gamma",xlab = "", cex.lab = 1, cex.axis = 1, main = "Second Survey")
arrows(y0 = c(Gamma_SS2$qD.LCL[1],Gamma_SS2$qD.LCL[2], Gamma_SS2$qD.LCL[3],Gamma_SS2$qD.LCL[4],Gamma_SS2$qD.LCL[5], Gamma_SS2$qD.LCL[6]),
       y1 = c(Gamma_SS2$qD.UCL[1],Gamma_SS2$qD.UCL[2], Gamma_SS2$qD.UCL[3],Gamma_SS2$qD.UCL[4],Gamma_SS2$qD.UCL[5], Gamma_SS2$qD.UCL[6]),
       x1 = c(1,2,3,5,6,7), x0 = c(1,2,3,5,6,7), 
       code = 3, angle = 90, length = 0.05, c("grey50"), lwd = 2)
points(y = c(Gamma_SS2$qD[1],Gamma_SS2$qD[2], Gamma_SS2$qD[3],Gamma_SS2$qD[4],Gamma_SS2$qD[5], Gamma_SS2$qD[6]), x = c(1,2,3,5,6,7), cex = 2, pch = c(15,16,17), col = c("sienna1","sienna3","sienna4","dodgerblue1","dodgerblue3", "dodgerblue4"))
axis(1, at = c(1,2,3,5,6,7), labels = c("30m ","120m","480m","30m","120m","480m"), las = 1, cex.axis = 1)
axis(1, at = c(2,6), labels = c("Fishless ","Fish"), las = 1, cex.axis = 1, line = 2, tick = F)
box(lwd = 2.5)
```

It does not seem to be any important differences among treatments.


#### Third Survey
First we get the estimated gamma diversity for each treatment for a sample size of four ponds.

First we computed the number of species in each treatment for a similar number of sampled ponds and its respective 95% confidence interval through sample-based rarefaction and extrapolation using the package `iNEXT`. What we call gamma diversity here is the realized species pool that is able to colonize ponds of a given treatment.
```{r gamma_SS3, cache = T}
absent_30_SS3 <- as.incfreq(t(decostand(com_SS3_predators[which(fish_isolation_SS3 == "030 absent"),], method = "pa")))
present_30_SS3 <- as.incfreq(t(decostand(com_SS3_predators[which(fish_isolation_SS3 == "030 present"),], method = "pa")))
absent_120_SS3 <- as.incfreq(t(decostand(com_SS3_predators[which(fish_isolation_SS3 == "120 absent"),], method = "pa")))
present_120_SS3 <- as.incfreq(t(decostand(com_SS3_predators[which(fish_isolation_SS3 == "120 present"),], method = "pa")))
absent_480_SS3 <- as.incfreq(t(decostand(com_SS3_predators[which(fish_isolation_SS3 == "480 absent"),], method = "pa")))
present_480_SS3 <- as.incfreq(t(decostand(com_SS3_predators[which(fish_isolation_SS3 == "480 present"),], method = "pa")))

all <- list(absent_30=absent_30_SS3 ,absent_120 =absent_120_SS3, absent_480=absent_480_SS3, present_30=present_30_SS3,present_120=present_120_SS3,present_480=present_480_SS3)

SS3_iNEXT <- iNEXT(all, datatype = "incidence_freq", q = 0, knots = 40,se = T, conf = 0.95,nboot =10000, size = c(1:4))

Gamma_SS3 <- rbind(absent_30 = SS3_iNEXT$iNextEst$absent_30[4,c(4,5,6)],
               absent_120 = SS3_iNEXT$iNextEst$absent_120[4,c(4,5,6)],
               absent_480 = SS3_iNEXT$iNextEst$absent_480[4,c(4,5,6)],
               present_30 = SS3_iNEXT$iNextEst$present_30[4,c(4,5,6)],
               present_120 = SS3_iNEXT$iNextEst$present_120[4,c(4,5,6)],
               present_480 = SS3_iNEXT$iNextEst$present_480[4,c(4,5,6)])
```

We can plot the estimates and respective confidence intervals.
```{r plot_SS3, dpi = 150, fig.height=5, fig.width=5}
plot(c(NA,NA,NA,NA,NA,NA),ylim = c(0,12), xlim = c(0.5,7.5),type = "p", xaxt = "n",ylab = "Gamma",xlab = "", cex.lab = 1, cex.axis = 1, main = "Third Survey")
arrows(y0 = c(Gamma_SS3$qD.LCL[1],Gamma_SS3$qD.LCL[2], Gamma_SS3$qD.LCL[3],Gamma_SS3$qD.LCL[4],Gamma_SS3$qD.LCL[5], Gamma_SS3$qD.LCL[6]),
       y1 = c(Gamma_SS3$qD.UCL[1],Gamma_SS3$qD.UCL[2], Gamma_SS3$qD.UCL[3],Gamma_SS3$qD.UCL[4],Gamma_SS3$qD.UCL[5], Gamma_SS3$qD.UCL[6]),
       x1 = c(1,2,3,5,6,7), x0 = c(1,2,3,5,6,7), 
       code = 3, angle = 90, length = 0.05, c("grey50"), lwd = 2)
points(y = c(Gamma_SS3$qD[1],Gamma_SS3$qD[2], Gamma_SS3$qD[3],Gamma_SS3$qD[4],Gamma_SS3$qD[5], Gamma_SS3$qD[6]), x = c(1,2,3,5,6,7), cex = 2, pch = c(15,16,17), col = c("sienna1","sienna3","sienna4","dodgerblue1","dodgerblue3", "dodgerblue4"))
axis(1, at = c(1,2,3,5,6,7), labels = c("30m ","120m","480m","30m","120m","480m"), las = 1, cex.axis = 1)
axis(1, at = c(2,6), labels = c("Fishless ","Fish"), las = 1, cex.axis = 1, line = 2, tick = F)
box(lwd = 2.5)
```
It seems that there is a higher gamma diversity in the intermediate isolation treatment for fishless ponds.





### Non-Predatory Insects
First, lets load the necessary data:
```{r 9}
data(com_SS2_non_predators,com_SS3_non_predators)
```


#### Second Survey
First we get the estimated gamma diversity for each treatment for a sample size of four ponds.

First we computed the number of species in each treatment for a similar number of sampled ponds and its respective 95% confidence interval through sample-based rarefaction and extrapolation using the package `iNEXT`. What we call gamma diversity here is the realized species pool that is able to colonize ponds of a given treatment.
```{r 10, cache = T}
absent_30_SS2 <- as.incfreq(t(decostand(com_SS2_non_predators[which(fish_isolation_SS2 == "030 absent"),], method = "pa")))
present_30_SS2 <- as.incfreq(t(decostand(com_SS2_non_predators[which(fish_isolation_SS2 == "030 present"),], method = "pa")))
absent_120_SS2 <- as.incfreq(t(decostand(com_SS2_non_predators[which(fish_isolation_SS2 == "120 absent"),], method = "pa")))
present_120_SS2 <- as.incfreq(t(decostand(com_SS2_non_predators[which(fish_isolation_SS2 == "120 present"),], method = "pa")))
absent_480_SS2 <- as.incfreq(t(decostand(com_SS2_non_predators[which(fish_isolation_SS2 == "480 absent"),], method = "pa")))
present_480_SS2 <- as.incfreq(t(decostand(com_SS2_non_predators[which(fish_isolation_SS2 == "480 present"),], method = "pa")))

all <- list(absent_30=absent_30_SS2 ,absent_120 =absent_120_SS2, absent_480=absent_480_SS2, present_30=present_30_SS2,present_120=present_120_SS2,present_480=present_480_SS2)

SS2_iNEXT <- iNEXT(all, datatype = "incidence_freq", q = 0, knots = 40,se = T, conf = 0.95,nboot =10000, size = c(1:4))

Gamma_SS2 <- rbind(absent_30 = SS2_iNEXT$iNextEst$absent_30[4,c(4,5,6)],
               absent_120 = SS2_iNEXT$iNextEst$absent_120[4,c(4,5,6)],
               absent_480 = SS2_iNEXT$iNextEst$absent_480[4,c(4,5,6)],
               present_30 = SS2_iNEXT$iNextEst$present_30[4,c(4,5,6)],
               present_120 = SS2_iNEXT$iNextEst$present_120[4,c(4,5,6)],
               present_480 = SS2_iNEXT$iNextEst$present_480[4,c(4,5,6)])
```

We can plot the estimates and respective confidence intervals.
```{r 11, dpi = 150, fig.height=5, fig.width=5}
plot(c(NA,NA,NA,NA,NA,NA),ylim = c(6,18), xlim = c(0.5,7.5),type = "p", xaxt = "n",ylab = "Gamma",xlab = "", cex.lab = 1, cex.axis = 1, main = "Second Survey")
arrows(y0 = c(Gamma_SS2$qD.LCL[1],Gamma_SS2$qD.LCL[2], Gamma_SS2$qD.LCL[3],Gamma_SS2$qD.LCL[4],Gamma_SS2$qD.LCL[5], Gamma_SS2$qD.LCL[6]),
       y1 = c(Gamma_SS2$qD.UCL[1],Gamma_SS2$qD.UCL[2], Gamma_SS2$qD.UCL[3],Gamma_SS2$qD.UCL[4],Gamma_SS2$qD.UCL[5], Gamma_SS2$qD.UCL[6]),
       x1 = c(1,2,3,5,6,7), x0 = c(1,2,3,5,6,7), 
       code = 3, angle = 90, length = 0.05, c("grey50"), lwd = 2)
points(y = c(Gamma_SS2$qD[1],Gamma_SS2$qD[2], Gamma_SS2$qD[3],Gamma_SS2$qD[4],Gamma_SS2$qD[5], Gamma_SS2$qD[6]), x = c(1,2,3,5,6,7), cex = 2, pch = c(15,16,17), col = c("sienna1","sienna3","sienna4","dodgerblue1","dodgerblue3", "dodgerblue4"))
axis(1, at = c(1,2,3,5,6,7), labels = c("30m ","120m","480m","30m","120m","480m"), las = 1, cex.axis = 1)
axis(1, at = c(2,6), labels = c("Fishless ","Fish"), las = 1, cex.axis = 1, line = 2, tick = F)
box(lwd = 2.5)
```

It does not seem to be any important differences among treatments.


#### Third Survey
First we get the estimated gamma diversity for each treatment for a sample size of four ponds.

First we computed the number of species in each treatment for a similar number of sampled ponds and its respective 95% confidence interval through sample-based rarefaction and extrapolation using the package `iNEXT`. What we call gamma diversity here is the realized species pool that is able to colonize ponds of a given treatment.
```{r 12, cache = T}
absent_30_SS3 <- as.incfreq(t(decostand(com_SS3_non_predators[which(fish_isolation_SS3 == "030 absent"),], method = "pa")))
present_30_SS3 <- as.incfreq(t(decostand(com_SS3_non_predators[which(fish_isolation_SS3 == "030 present"),], method = "pa")))
absent_120_SS3 <- as.incfreq(t(decostand(com_SS3_non_predators[which(fish_isolation_SS3 == "120 absent"),], method = "pa")))
present_120_SS3 <- as.incfreq(t(decostand(com_SS3_non_predators[which(fish_isolation_SS3 == "120 present"),], method = "pa")))
absent_480_SS3 <- as.incfreq(t(decostand(com_SS3_non_predators[which(fish_isolation_SS3 == "480 absent"),], method = "pa")))
present_480_SS3 <- as.incfreq(t(decostand(com_SS3_non_predators[which(fish_isolation_SS3 == "480 present"),], method = "pa")))

all <- list(absent_30=absent_30_SS3 ,absent_120 =absent_120_SS3, absent_480=absent_480_SS3, present_30=present_30_SS3,present_120=present_120_SS3,present_480=present_480_SS3)

SS3_iNEXT <- iNEXT(all, datatype = "incidence_freq", q = 0, knots = 40,se = T, conf = 0.95,nboot =10000, size = c(1:4))

Gamma_SS3 <- rbind(absent_30 = SS3_iNEXT$iNextEst$absent_30[4,c(4,5,6)],
               absent_120 = SS3_iNEXT$iNextEst$absent_120[4,c(4,5,6)],
               absent_480 = SS3_iNEXT$iNextEst$absent_480[4,c(4,5,6)],
               present_30 = SS3_iNEXT$iNextEst$present_30[4,c(4,5,6)],
               present_120 = SS3_iNEXT$iNextEst$present_120[4,c(4,5,6)],
               present_480 = SS3_iNEXT$iNextEst$present_480[4,c(4,5,6)])
```

We can plot the estimates and respective confidence intervals.
```{r 13, dpi = 150, fig.height=5, fig.width=5}
plot(c(NA,NA,NA,NA,NA,NA),ylim = c(6,18), xlim = c(0.5,7.5),type = "p", xaxt = "n",ylab = "Gamma",xlab = "", cex.lab = 1, cex.axis = 1, main = "Third Survey")
arrows(y0 = c(Gamma_SS3$qD.LCL[1],Gamma_SS3$qD.LCL[2], Gamma_SS3$qD.LCL[3],Gamma_SS3$qD.LCL[4],Gamma_SS3$qD.LCL[5], Gamma_SS3$qD.LCL[6]),
       y1 = c(Gamma_SS3$qD.UCL[1],Gamma_SS3$qD.UCL[2], Gamma_SS3$qD.UCL[3],Gamma_SS3$qD.UCL[4],Gamma_SS3$qD.UCL[5], Gamma_SS3$qD.UCL[6]),
       x1 = c(1,2,3,5,6,7), x0 = c(1,2,3,5,6,7), 
       code = 3, angle = 90, length = 0.05, c("grey50"), lwd = 2)
points(y = c(Gamma_SS3$qD[1],Gamma_SS3$qD[2], Gamma_SS3$qD[3],Gamma_SS3$qD[4],Gamma_SS3$qD[5], Gamma_SS3$qD[6]), x = c(1,2,3,5,6,7), cex = 2, pch = c(15,16,17), col = c("sienna1","sienna3","sienna4","dodgerblue1","dodgerblue3", "dodgerblue4"))
axis(1, at = c(1,2,3,5,6,7), labels = c("30m ","120m","480m","30m","120m","480m"), las = 1, cex.axis = 1)
axis(1, at = c(2,6), labels = c("Fishless ","Fish"), las = 1, cex.axis = 1, line = 2, tick = F)
box(lwd = 2.5)
```
It seems that there is a higher gamma diversity in the intermediate isolation treatment for fishless ponds.



